|

### 2022-11-03 revision_letter.Rmd
capitalize
more ideas

thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
In the following we address your and each reviewers' concerns point-by-point.

@@

This is our response.

@@

@@

>>>>

Thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
In the following we address your and each reviewers' concerns point-by-point.

@@

This is our response: For example, instructors can include accessibility as one of their evaluation criteria for course assignments or make it as a chance to obtain bonus credits for the students' visualization work.

@@

This is our response: need to create a section dededicated to a11y, and say that we are presenting this paper as a demonstration how we integrated a11y into our courses.

@@

This is our response: good point so it is critical to share the same principle across different and with upper level courses .
